\section{Commonalities}

This section outlines the shared elements across the different games in the product family, including core mechanics, UI components, and gameplay goals.

\subsection{Dice Rolls}
A fundamental aspect of the game is its reliance on dice rolls. All variants will incorporate dice rolling as a primary mechanic, with corresponding UI elements to visually represent the action, ensuring consistency across game versions.

\subsection{Yahtzee Hands}
The scoring system in each game variant will be based on Yahtzee-style hands. While the specific scoring mechanics and available hands may vary slightly, the core objective of rolling a hand that aligns with predefined scoring categories remains consistent throughout all versions.

\subsection{Score Sheet Structure}
Similar to the Yahtzee Hands mechanic, the structure of the score sheet will be uniform across all game variants. This provides players with a familiar interface and ensures consistency in tracking scores.

\subsection{Simultaneous Play}
The game is designed for real-time play rather than a turn-based system. Players will always be engaged in the same stage of rolling, preventing any strategic advantage in head-to-head game variants.

\subsection{2-Player or Single-Player Only}
None of the game variants will support more than two human players. The focus will remain on single-player modes or head-to-head matchups with only two participants.

\subsection{Always Playing Against an Opponent}
Players will never play in isolation to achieve the highest possible score. Instead, each game will involve competing either against another player or against a predetermined computer score criterion, reinforcing the competitive nature of the gameplay.
