\section{Variabilities}

This section details the variabilities between the different games in the product family, including changes in UI elements, game goals, and core mechanics.

\subsection{Number of Dice}
The number of dice used in the game can vary between different versions. Some variants may increase or decrease the number of dice to adjust the complexity and strategy of the game.

\subsection{Sides on Dice}
The number of sides on each dice can differ across game variants. This allows for customization of gameplay, where different variants may feature dice with more or fewer sides, influencing the probability and outcomes of each roll.

\subsection{Individual Sides}
The specific values or symbols on the sides of each dice can vary between versions. This variability provides an opportunity to introduce different themes or scoring dynamics depending on the game's rules.

\subsection{Scoring Calculation}
How points are calculated for different hands and the influence of dice rolls on the final score can be customized in different game variants. This allows for changes in how specific hands are valued and how scoring impacts the overall gameplay strategy.

\subsection{Time Per Turn}
The amount of time a player has to roll the dice and make their selection can be adjusted between variants. Time limits can vary, creating different levels of pressure and pacing in the game.

\subsection{Hand Restrictions}
Some game variants may restrict certain hands from being scored or may allow hands to be scored multiple times. These variations provide flexibility in game strategy and scoring dynamics.
